### 2023-08-23 README.rmd
small changes in documentation

>>>>

#### Reproductibility

Clustering methods like CMeans depend on the initial centers selected. In `geocmeans`, they are selected randomly, and two runs of the functions can yield different results. To facilitate the reproductibility of the results, the main functions of the package (`CMeans`, `GFCMeans`, `SFCMeans`, `SGFCMeans`, `selectParameters`, `selectParameters.mc`) have a `seed` parameter. It can be set by the user to ensure that the results of the functions are exactly the same.
